---
title: "Predicting Quality of Red Wine"
author: "Lena Nguyen"
output: 
  html_document:
    theme: 'flatly'
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = FALSE, echo = FALSE, warning = FALSE)

library(dplyr)
library(readr)
library(ggplot2)
library(caret)
library(corrplot)
```
## Introduction
The two [datasets](http://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/) are related to red and white variants of the Portuguese "Vinho Verde" wine. The 'quality' column in the datasets is the score given by experts for wine quality. The wine quality score varies between 0 (very bad) and 10 (very excellent). The other 11 columns in the data are measured chemical properties of the wine. 

For the purpose of this exercise, let's focus on the white wine dataset. The white wine dataset has *4898 observations*. We first want to explore the dataset and look at what chemical properties correlate with a higher wine quality grading for red wine. 

```{r load_data}
url <- 'http://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality-white.csv'

## Read in the red wine dataset
white_wine <- read_delim(url, delim = ';') %>%
  # replace spaces with '.' in column names
  rename_all(funs(make.names(.)))
```

## Explore the Data
### Wine Quality
Looking at the distribution of wine quality ratings, there are many more average wines than bad or excellent wines.

```{r eda, include = TRUE}
# Distribution of wine quality ratings
ggplot(white_wine, aes(x = factor(quality))) +
  geom_bar(stat = "count", position = "dodge") +
  labs(x = 'Wine Quality', title = "Distribution of White Wine Quality Ratings") +
  theme_minimal()
```

### Chemical Properties and Wine Quality

White wine quality seems to be positively correlated with *alcohol* level and somehwat negatively correlated to *density*.

```{r corr, include = TRUE}
# Look at the correlation between variables
correlations <- cor(white_wine, method = "pearson")

corrplot(correlations, number.cex = .9, method = "square", 
         hclust.method = "ward", order = "FPC",
         type = "full", tl.cex=0.8, tl.col = "black")
```

